---
title: "Developing Data Products"
author: "Ram"
date: "17/01/2021"
output:
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## A Shiny Application

- The shiny application pitched in this presentation is here [https://ramprashanth97.shinyapps.io/project/]

- The Shiny app source code is here [https://github.com/ramprashanth97/Developing-Data-Products---Course-Project]

## What does the app do?
- Allows you to visualise the areas of US states in square miles using the US State Facts and Figures dataset. 

- You can use sliders to select an area range to display and checkboxes to show different regions

- The output is an interactive map of the US showing the states that satisfy the selected criteria.

## Under the hood
```{r}
states <- data.frame(state.name, state.area, state.region,
                     hover=paste0(state.name, ": ", 
                                               state.area, " square miles"))
states$hover <- as.character(states$hover)
```

- A data frame called `states` was created using the vectors from the US Facts and Figures Dataset.

- A fourth column (`hover`) was added for the interactivity of the map.

```{r, echo=TRUE}
head(states)
```



## Output
- The slider values and checkbox values are used to filter the dataset using the `state.name` and `state.region` columns before creating the map.

- The output is a googlevis interactive map.

- The states turn green when they satisfy the selected criteria (slider and checkboxes)

- When each green state is hovered over, the name and area of the state is displayed.
